Microbial Interactions as Drivers of a Nitrification Process in a Chemostat

### 2020-08-04 tex/Article_Processes.tex
adding article processes format

\documentclass[3p,times]{article}

\usepackage[margin=0.7in]{geometry}

\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage[version=4]{mhchem}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\I}{\mathcal{I}}
\DeclareMathOperator{\diag}{diag}
\declaretheorem[name=Theorem]{thm}
\declaretheorem[name=Lemma]{lemma}
\newtheorem{defn}{Definition}
\newtheorem{hypo}{H}
\usepackage[figuresright]{rotating}

\graphicspath{{Images/}}

\begin{document}

\title{Microbial interactions as drivers of a nitrification process in a chemostat}

\author{Pablo Ugalde-Salas, Héctor Ramírez C., Jérôme Harmand, Elie Desmond-Le Quéméner}
\date{}
\maketitle

\begin{abstract}
	This article deals with the inclusion of microbial ecology measurements such as abundances of operative taxonomic units in bioprocess modelling. The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting where a nitrification process was operated for over 500 days. The limitations and the insights of such an approach are discussed. In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of data from genetic sequencing in chemostat models is presented. The optimal tracking revisits the data used in the aforementioned chemostat setting. The method is able to reconstruct the different forms of nitrogen in the reactor by using the abundances of the operative taxonomic units, even though the synthesized control can not be guaranteed to be optimal. 
\end{abstract}

@@

Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}. Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics presented by Song \textit{et al.}\cite{Song2014}, this articles deals with population-based approaches where species are taken as the interacting units.

The classical ecological concept of species and niche in the microbial world is an elusive one: in the macro world one can clearly identify one species of another for reproductive reasons and their ability to give birth to offspring. In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}. Therefore as an ecological problem is hard to precise the 'niche' of 'microbial species'. These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of 16S rDNA marker gene. In the past years considerable efforts have been made to measure the bacterial community composition. Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}. The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances over time. In other words, while most models used in bioengineering are functional- in the sense they consider only one species per biological reaction considered- this work is a first attempt to merge classical population-based models used in ecology and those used by engineers in biotechnology.

As a departing point, the work of Dumont et al.\cite{Dumont2016} is presented in section 2. They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model\cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints. Section 3 inspects the model through a mathematical analysis. Some interesting outputs of this analysis are that the number of possible equilibrium points grows exponentially with the number of species, coexistence can be achieved within the same functional group, and bi-stability may arise. In section 4 the concept of interaction function is developed such that it generalizes the gLV model. For approximating the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data. The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations\cite{Cimen2008}. In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al}\cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}. This approach explicitly assumes that dynamics of complex ecosystems are driven by interactions, that are the results of feedback loops of each species on the growth rate of others. The method shows that by following the community dynamics one can propose a growth rate that reconstructs the substrates dynamics. The article ends with a discussion on the scope of applicability and perspectives of the method .

@@

Notations used throughout the article:
\begin{enumerate}
	\item $n$: the number of OTU considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$. In the example $G_1$ corresponds to ammonium oxidizing bacteria (AOB) and $G_2$ corresponds to nitrite oxidizing bacteria (NOB).
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$. In the example $s_1$ represents ammonium.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. In the example $s_2$ represents nitrite. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$. In the example $s_3$ represents nitrate.
	\item $s_{in}$: entry concentration of substrate $1$ in $[g/l]$. May depend on time $s_{in} = s_{in}(t)$.
	\item $s$:  vector $(s_1,s_2,s_3)^\top$. Referred to as metabolites.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: dilution rate of the continuous reactor in $[1/day]$. May depend on time $D=D(t)$.
	\item $y_{i}$: yield of grams of OTU $i$ formed per gram of substrate consumed. 
	\item $y_{s_i/x_j}$: yield of grams of substrate $s_i$ consumed/produced per gram of OTU $j$ formed. If negative it represents consumption, if positive it represents production.
	\item $Y$: matrix containing all yields such that $Y_{ij} = y_{s_i/x_j}$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
	\item Let $M$ be a matrix, then $M_{i\bullet}$ represents the $i$-th row of matrix $M$.
	\item Let $S$ be a finite set with $m \in \N$ elements. Then $\vert S \vert := m$. 
	\item Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
	\begin{align}
	\begin{array}{rc}
	\diag:\R^n \rightarrow & \mathbb{M}_{n\times n}(\R)\\
	& \\
	v \rightarrow & \begin{pmatrix}
	v_1 & 0 & \dots & 0 \\
	0 & v_2 & \ddots & \vdots\\ 
	\vdots & \ddots & \ddots& 0 \\
	0 & \dots &0 & v_n 
	\end{pmatrix}
	\end{array} \label{diag_operator}
	\end{align}
\end{enumerate}

@@

The situation is described as simplified reactions \eqref{Reaction1} and \eqref{Reaction2}. The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather they represent the direction of the bioprocess and the proportions of different consumed and formed compounds of interest. The terms $y_i$ are known as yields, they represent the quantity of g of biomass produced per g of substrate consumed by  OTU $i$. For example in the case of reaction \eqref{Reaction1}, one gram of $s_1$ is consumed, one gram of $s_2$ and $y_{x_i/s_1}$ grams of dry biomass of OTU $i$ are produced. 
\begin{align}
\label{Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
\label{Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
\end{align}
However for expressing the system of differential equations further below, the terms $y_{s_i/x_j}$ are used. They express the grams of substrate $s_i$ consumed (negative sign) or produced (positive sign) per gram of OTU $j$ formed. They are related to $y_i$ as seen in table \ref{yields table}. This defines the stoichiometry matrix $Y \in \R^{3 \times n}$, such that $Y_{ij} = y_{s_i/x_j}$.
\begin{table}[h]
	\centering
	\begin{tabular}{|l|l|l|}
		\hline
		\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Yields per \\ Biomass formed\end{tabular}} & \multicolumn{1}{c|}{$j \in G_1$} & \multicolumn{1}{c|}{$j \in G_2$} \\ \hline   \rule{0pt}{3.5ex}
		$y_{s_1/x_j}$ & $-\dfrac{1}{y_j}$ & $0$ \\  \hline   \rule{0pt}{3.5ex}
		$y_{s_2/x_j}$ & $\dfrac{1}{y_j}$  & $-\dfrac{1}{y_j}$ \\ \hline   \rule{0pt}{3.5ex}
		$y_{s_3/x_j}$ & $0$  & $\dfrac{1}{y_j}$  \\ \hline
	\end{tabular}
	\caption{Relationship of $y_{s_i/x_j}$ with $y_j$.}
		\label{yields table}
\end{table}

@@

\subsection{Kinetic Equations}
In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rates seen in equations \eqref{gLV growth1} and \eqref{gLV growth2} were calibrated against experimental data for the two most abundant OTU of each functional group.

\begin{align}
\label{gLV growth1}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
\label{gLV growth2}\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2 
\end{align}

The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU, while the term $\bar{\mu}_i\dfrac{s_j}{K_i + s_j}$ is a Monod growth expression, where $\bar{\mu}_i$ represents the maximum growth rate, and $K_i$ the half saturation constant \cite{monod1942recherches}. Let $A$ denote the matrix
with entries $a_{ij}$ hereafter referred to as the interaction matrix. Dumont\textit{ et al.} did not analyse their model but simply provided several simulations using parameter values identified from experimental data. The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}.

@@

\subsection{Properties of the system}

@@

\begin{restatable}{lemma}{systembounds}
	\label{l1}
	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists positive scalars $M_1$, $M_2$, and $M_3$ such that solutions to \eqref{system} satisfy the following inequalities:
	\begin{align}
	&\sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1 \leq M_1 \\
	&\sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 +s_2 \leq M_2 \\
	&s_1 + s_2 + s_2 \leq M_3
	\end{align}
\end{restatable}

@@

\begin{restatable}{thm}{wellposedness}
	\label{theoWellPosedness}
	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth1} and \eqref{gLV growth2}, remain in $\Omega$ and are bounded.
\end{restatable}

@@

@@

@@

\subsection{Tracking Problem reformulation and details}

>>>>

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[processes,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, applmech, applnano, applsci, arts, asc, asi, atmosphere, atoms, automation, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomedinformatics, biomimetics, biomolecules, biosensors, bloods, brainsci, breath, buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cyber, dairy, data, dentistry, dermatopathology, designs, diabetology, diagnostics, digital, diseases, diversity, drones, earth, econometrics, ecologies, economies, education, ejbc, ejihpe, electricity, electrochem, electronicmat, electronics, endocrines, energies, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, fuels, futureinternet, futurephys, galaxies, games, gardens, gases, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, hearts, heritage, highthroughput, horticulturae, humanities, hydrogen, hydrology, ijerph, ijfs, ijgi, ijms, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jce, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jne, jnt, jof, joitmc, journalmedia, jpm, jrfm, jsan, land, languages, laws, life, literature, livers, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, ijns, neurosci, neuroglia, nitrogen, notspecified, nutrients, obesities, oceans, ohbm, osteology, optics, organics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, pollutants, polymers, polysaccharides, preprints , proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, religions, remotesensing, reprodmed, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, surfaces, surgeries, suschem, sustainability, world, symmetry, systems, technologies, telecom, test, tourismhosp, toxics, toxins, transplantology, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj, women

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2020}
\copyrightyear{2020}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx,epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Microbial Interactions as Drivers of a Nitrification Process in a Chemostat}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-9224-291X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Pablo Ugalde-Salas $^{1,\dagger,\ddagger}$\orcidA{\orcidauthorA}, Héctor Ramírez C. $^{1,\ddagger}$, Jérôme Harmand, and Elie Desmond-Le Quéméner $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{ 	This article deals with the inclusion of microbial ecology measurements such as abundances of operative taxonomic units in bioprocess modelling. The first part presents the mathematical analysis of a model that may be framed within the class of Lotka-Volterra models fitted to experimental data in a chemostat setting where a nitrification process was operated for over 500 days. The limitations and the insights of such an approach are discussed. In the second part,  the use of an optimal tracking technique (developed within the framework of control theory) for the integration of data from genetic sequencing in chemostat models is presented. The optimal tracking revisits the data used in the aforementioned chemostat setting. The method is able to reconstruct the different forms of nitrogen in the reactor by using the abundances of the operative taxonomic units, even though the synthesized control can not be guaranteed to be optimal. }

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage[version=4]{mhchem}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\I}{\mathcal{I}}
\DeclareMathOperator{\diag}{diag}
%\declaretheorem[name=Theorem]{thm}
%\declaretheorem[name=Lemma]{lemma}
\newtheorem{defn}{Definition}
\newtheorem{hypo}{H}
\usepackage[figuresright]{rotating}

\graphicspath{{Images/}}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

@@

Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}. Using the terminology from the thorough review in current methodologies on the deterministic modelling approaches of microbial community dynamics presented by Song \textit{et al.} \cite{Song2014}, this articles deals with population-based approaches where species are taken as the interacting units.

The classical ecological concept of species and niche in the microbial world is an elusive one: in the macro world one can clearly differentiate one species from another for reproductive reasons and their ability to give birth to offspring. In the case of bacteria and archea, reproduction goes simply by binary fission and exchange of some functional genes (e.g. the ability to synthesize or metabolize substances) can be acquired in evolutionary scale through lateral gene transfer \cite{Boucher2003}. Therefore as an ecological problem is hard to precise the 'niche' of 'microbial species'. These obstacles can be circumvented by considering the microbiologist concept of operative taxonomic unit (OTU) based on the clustering of organisms sharing similar sequences of the 16S rDNA marker gene. In the past years considerable efforts have been made to measure the bacterial community composition. Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA have become a standard tool for studying  microbial diversity \cite{FERRERA2016790}. The contribution of this article is a new method to integrate the microbial community measurements in chemostat models, based on any sequencing or fingerprinting technique that can quantify the species abundances over time. In other words, while most models used in bioengineering are functional- in the sense they consider only one species per biological reaction considered- this work is a first attempt to merge classical population-based models used in ecology and those used by engineers in biotechnology.

As a departing point, the work of Dumont\textit{ et al.} \cite{Dumont2016} is presented in section 2. They modelled a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression and fitted their model using absolute abundances of the major OTU identified by molecular fingerprints. Section 3 inspects the model through a mathematical analysis. Some interesting outputs of this analysis are that the number of possible equilibrium points grows exponentially with the number of species, coexistence can be achieved within the same functional group, and bi-stability may arise. In section 4 the concept of interaction function is developed such that it generalizes the gLV model. For approximating the interaction function a method of optimal control theory was adapted: The growth rate of each species is modulated by a constrained regular control of the system, thus the growth rate of each OTU is corrected in order to fit the experimental data. The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species; the method involves solving state-dependent Ricatti equations \cite{Cimen2008}. In section 5 the methodology from section 4 is applied to the data from the experiments performed by Dumont \textit{et al.} \cite{Dumont2009} and not just to the most abundant species as it was the case of the model analysed in section 3 \cite{Dumont2016}. This approach explicitly assumes that dynamics of complex ecosystems are driven by interactions, that are the results of feedback loops of each species on the growth rate of others. The method shows that by following the community dynamics one can propose a growth rate that reconstructs the substrates dynamics. The article ends with a discussion on the scope of applicability and perspectives of the method .

@@

Notations used throughout the article:
\begin{enumerate}
	\item $n$: the number of OTU considered.
	\item $n_i, \, i \in \{1,2\}$: the number of OTU in functional group $G_i$. In the example $G_1$ corresponds to ammonium oxidizing bacteria (AOB) and $G_2$ corresponds to nitrite oxidizing bacteria (NOB).
	\item Let $m$ be an interger then $[m]:=\{1,\dots,n \}$. 
	\item $x_i$ :  is the concentration of OTU $i$ measured in $[g/l]$. $i \in [n]$. 
	\item $x$: vector $(x_1,\dots,x_n)^\top$.
	\item $s_1$ : concentration of substrate 1 in $[g/l]$. In the example $s_1$ represents ammonium.
	\item $s_2$ : concentration of substrate 2 in $[g/l]$. In the example $s_2$ represents nitrite. 
	\item $s_3$ : concentration of substrate 3 in $[g/l]$. In the example $s_3$ represents nitrate.
	\item $s_{in}$: entry concentration of substrate $1$ in $[g/l]$. May depend on time $s_{in} = s_{in}(t)$.
	\item $s$:  vector $(s_1,s_2,s_3)^\top$. Referred to as metabolites.
	\item $\I_i(t,x)$ : Interaction function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu_i(s,x)$ : growth function of OTU $i \in \{1,\dots,n\}$.
	\item $\mu = (\mu_1(s,x), \dots, \mu_n(s,x))$ vector containing the growth function of every OTU.
	\item $D$: dilution rate of the continuous reactor in $[1/day]$. May depend on time $D=D(t)$.
	\item $y_{i}$: yield of grams of OTU $i$ formed per gram of substrate consumed. 
	\item $y_{s_i/x_j}$: yield of grams of substrate $s_i$ consumed/produced per gram of OTU $j$ formed. If negative it represents consumption, if positive it represents production.
	\item $Y$: matrix containing all yields such that $Y_{ij} = y_{s_i/x_j}$.
	\item For integers $m_1$ and $m_2$ and $a \in \R$, $a_{m_1 \times m_2}$ represents a matrix of $m_1$ rows and $m_2$ columns with $a$ in every entry. 
	\item Let $m$ be an integer then $I_m$ is the identity matrix of size $m$.
	\item Let $M$ be a matrix, then $M_{i\bullet}$ represents the $i$-th row of matrix $M$.
	\item Let $S$ be a finite set with $m \in \N$ elements. Then $\vert S \vert := m$. 
	\item Given a vector $v=(v_1,\dots, v_n)\in \R^n$, the function $\diag(v)$ stands for:
	\begin{align}
	\begin{array}{rc}
	\diag:\R^n \rightarrow & \mathbb{M}_{n\times n}(\R)\\
	& \\
	v \rightarrow & \begin{pmatrix}
	v_1 & 0 & \dots & 0 \\
	0 & v_2 & \ddots & \vdots\\ 
	\vdots & \ddots & \ddots& 0 \\
	0 & \dots &0 & v_n 
	\end{pmatrix}
	\end{array} \label{inter:diag_operator}
	\end{align}
\end{enumerate}

@@

The situation is described as simplified reactions \eqref{inter:Reaction1} and \eqref{inter:Reaction2}. The reactions are simplified in the sense that they do not attempt to represent a balanced chemical reaction, rather they represent the direction of the bioprocess and the proportions of different consumed and formed compounds of interest. The terms $y_i$ are known as yields, they represent the quantity of g of biomass produced per g of substrate consumed by  OTU $i$. For example in the case of reaction \eqref{inter:Reaction1}, one gram of $s_1$ is consumed, one gram of $s_2$ and $y_{x_i/s_1}$ grams of dry biomass of OTU $i$ are produced. 
\begin{align}
\label{inter:Reaction1} \tag{R G1} s_1 \stackrel{\mu_i(s,x)}{\longrightarrow} s_2 + y_ix_i \quad \forall i \in G_1 \\
\label{inter:Reaction2} \tag{R G2} s_2\stackrel{\mu_i(s,x)}{\longrightarrow} s_3 + y_ix_i \quad \forall i \in G_2
\end{align}
However for expressing the system of differential equations further below, the terms $y_{s_i/x_j}$ are used. They express the grams of substrate $s_i$ consumed (negative sign) or produced (positive sign) per gram of OTU $j$ formed. They are related to $y_i$ as seen in table \ref{yields table}. This defines the stoichiometry matrix $Y \in \R^{3 \times n}$, such that $Y_{ij} = y_{s_i/x_j}$.
\begin{table}[h]
	\centering
	\begin{tabular}{|l|l|l|}
		\hline
		\multicolumn{1}{|c|}{\begin{tabular}[c]{@{}c@{}}Yields per \\ Biomass formed\end{tabular}} & \multicolumn{1}{c|}{$j \in G_1$} & \multicolumn{1}{c|}{$j \in G_2$} \\ \hline   \rule{0pt}{3.5ex}
		$y_{s_1/x_j}$ & $-\dfrac{1}{y_j}$ & $0$ \\  \hline   \rule{0pt}{3.5ex}
		$y_{s_2/x_j}$ & $\dfrac{1}{y_j}$  & $-\dfrac{1}{y_j}$ \\ \hline   \rule{0pt}{3.5ex}
		$y_{s_3/x_j}$ & $0$  & $\dfrac{1}{y_j}$  \\ \hline
	\end{tabular}
	\caption{Relationship of $y_{s_i/x_j}$ with $y_j$.}
	\label{yields table}
\end{table}

@@

\subsection{Kinetic Equations}
In the work of Dumont \textit{et al.} \cite{Dumont2016} the growth rates seen in equations \eqref{gLV growth} were calibrated against experimental data for the two most abundant OTU of each functional group.

\begin{align}
\label{gLV growth} \begin{array}{lc}
\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_1}{K_i + s_1}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_1 \\
\mu_i(s,x) &= \bar{\mu}_i \dfrac{s_2}{K_i + s_2}\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right) \quad \forall i \in G_2
\end{array}  
\end{align}

The term $\left(1+\sum \limits_{j\in [n]} a_{ij} x_{j} \right)$ accounts for pairwise interactions affecting the growth rate of each OTU, while the term $\bar{\mu}_i\dfrac{s_j}{K_i + s_j}$ is a Monod growth expression, where $\bar{\mu}_i$ represents the maximum growth rate, and $K_i$ the half saturation constant \cite{monod1942recherches}. Let $A$ denote the matrix
with entries $a_{ij}$ hereafter referred to as the interaction matrix. Dumont\textit{ et al.} did not analyse their model but simply provided several simulations using parameter values identified from experimental data. The following section of this article deals with the mathematical analysis of model \eqref{system} with growth rates given by \eqref{gLV growth}.

@@

\subsection{Properties of the system}
\label{Properties_of_the_system}

@@

\begin{Lemma}
	\label{l1}
	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists positive scalars $M_1$, $M_2$, and $M_3$ such that solutions to \eqref{system} satisfy the following inequalities:
	\begin{align}
	&\sum \limits_{i \in G_1} \frac{1}{y_i}x_i + s_1 \leq M_1 \\
	&\sum \limits_{i \in G_2} \frac{1}{y_i}x_i + s_1 +s_2 \leq M_2 \\
	&s_1 + s_2 + s_2 \leq M_3
	\end{align}
\end{Lemma}

@@

\begin{Lemma}
	\label{theoWellPosedness}
	For initial conditions $(x_1(0),\dots,x_n(0),s_1(0),s_2(0),s_3(0)))\in \Omega$, there exists a constant $M>0$ such that for every matrix $A$ satisfying $\Vert A \Vert_{\infty} \leq M $, the solutions of system \eqref{system} with growth rates given by \eqref{gLV growth}, remain in $\Omega$ and are bounded.
\end{Lemma}

@@

\subsection{Both functional groups are present}

@@

\subsection{Washout of $G_2$}

@@

\section{Tracking Problem reformulation and details}
